An analysis of underlying relationships between factors related to operating costs and revenue in Australian vineyards.

### 2023-12-18 article.tex
mardi edits

 The Australian wine industry is a major part of Australia's agricultural sector. As global demands change and new pressures on the industry present themselves, a more sustainable approach is needed. Through a nationwide data set, collected over ten years, we link key variables in determining vineyard operational costs and revenue through the use of XGBoost. We use a measure of relative importance to show the interrelated nature of these variables and the comparative influence they have on one another. We present these connections through the use of Sankey and Chord diagrams to show the important predictors of revenue and operating costs and their strong interrelatedness. Furthermore, we connect these variables to different wine regions, highlighting the complex influence of location on the use of different resources. The study provides valuable insights into the multifaceted dynamics governing operational costs and revenue, illustrating how factors such as water and fuel use impacts on operational costs and how different seasonal events affect these operations.

@@

Historically strong demands for Australian wine have helped to create a thriving industry. However, recent pressures brought on by a loss of tourism and labour due to the COVID-19 pandemic, the global freight crisis, war in Europe, tariffs and rising inflation have negatively affected the industry's outlook \citep{wineaustraliaNationalVintageReport2021,wineaustraliaAustralianWineProduction2021}. The 2021-2022 financial year alone saw a decline of 19\% in exports solely due to tariffs \citep{wineaustraliaNationalVintageReport2022}. A greater understanding of the different underlying conditions leading to improved performance in agricultural productivity and sustainability at scale is key to making data-informed decisions increase a nation's agricultural sustainability \citep{oecdInnovationProductivitySustainability2019}. Specifically within the Australian wine and vine industry, there is a need to further understand the driving relationships between resource use and economic output, which can help to determine more cost effective and efficient methods and develop benchmarks with local growers \citep{lukemanciniUnderstandingAustralianWine2020}.
\par
An unprecedented amount of data regarding the Australian winegrowing industry has been collected through Sustainable Winegrowing Australia, offering the potential for new insights into the driving economic forces of the Australian wine industry. A major part of the potential for insight within this dataset comes from the incorporation of operating costs and grape revenue from grape sales within the data. In this paper, we use data to study economic outcomes and their statistical relationships to vineyards' utilisation of the resources. We further compare the relationships between different resources to address the extensive collinearity found within the data \citep{chenXGBoostScalableTree2016}. We adopt  a popular, relatively new machine learning method, XGBoost, for this analysis because it is able to overcome multicollinearity as well as highlight the level of importance that predictor variables have on response variables.

@@

\subsection{Data}\label{Data}
% 6049 samples - total
% 58 regions
% 10 years
% 
% 853 with reported profits
% 46 regions
% reported since 2018
Data used in this analysis were obtained from Sustainable Winegrowing Australia (SWA), Australia's national wine industry sustainability program. SWA aims to support grape growers and winemakers in demonstrating and improving their sustainability \citep{swaSustainableWingrowingAustralia2022}. Data recorded by SWA are entered manually by winegrowers using a web based interface tool. A total of 6049 observations were collected from 2012/2013 to 2021/2022 financial years, with each observation comprising 23 variables reflecting a vineyard's state for the given year (see Table \ref{tab:vars}). 
\par
\begin{table}[] 
 \label{tab:vars}
 \caption{Summary of variables used in the analysis. The recorded column indicate the number of values that were either greater than zero or that were not missing.}\label{tab:summary}
 \small
 \begin{tabular}{@{}ccccl@{}}
  \toprule
  \textbf{Variable} & \textbf{Units} & \textbf{Recorded} & \textbf{Number of Classes} & \\ \midrule
  Water Used & Mega Litres & 5846 & & \\
  Diesel & Litres & 5585 & & \\
  Biodiesel & Litres & 25 & & \\
  LPG & Litres & 958 & & \\
  Herbicide Spray & Times per year & 2026 & & \\
  Year & Class & 6049 & 10 & \\
  Disease & Class & 6049 & 2 & \\
  Region & Class & 6049 & 58 & \\
  Solar & Kilowatt Hours & 622 & & \\
  Irrigation Type & Class & 6049 & 20 & \\
  Petrol & Litres & 4309 & & \\
  Slashing & Times per year & 2290 & & \\
  Yield & Tonnes & 5935 & & \\
  Irrigation Energy & Class & 6049 & 16 & \\
  Area Harvested & Hectares & 6049 & & \\
  Electricity & Kilowatt Hours & 1014 & & \\
  Insecticide Spray & Times per year & 1092 & & \\
  Fertiliser & KGs of Nitrogen & 795 & & \\
  Fungicide Spray & Times per year & 2260 & & \\
  Cover Crop & Class & 6049 & 32 & \\
  Water Type & Class & 6049 & 39 & \\
  Grape Revenue & AUD & 853 & & \\
  Operating Costs & AUD & 853 & & \\ \bottomrule
  \end{tabular}
\end{table}
\normalsize
The data originally contained only two multiclass variables: year and region. For this case study, related binary variables, such as the use of river water and the use of dam water, were combined to create multiclass variables such as water source. Further details about these variables, their classes and their frequency is available in the Appendix.
\par
The variable Region represented one of the 65 Geographical Indicator Regions (GI Region) used to describe different unique localised traits of vineyards across Australia \citep{hallidayAustralianWineEncyclopedia2009,oliverReviewSoilPhysical2013,soarClimateDriversRed2008}. Each region is explicitly defined under the Wine Australia Corporation Act of 1980 \citep{attorney-generalsdepartmentWineAustraliaCorporation2010}.
\par

@@

Region was a highly informative variable based on measures of importance for both operating cost and revenue. As noted above, Region was the third most important variable for determining revenue. The Barossa Valley region and Tasmania were the two most important regions in relation to revenue; these two regions are considered to be some of the highest revenue per hectare regions in Australia \citep{wineaustraliaNationalVintageReport2022}. These two regions are also relative opposites in winegrowing climates with the Barossa having a warm and dry climate focussing on Shiraz grapes and Tasmania having a cool wet climate that favours Pinot. 
\par
As also noted, above Region was also a key determinant of operating costs. Again Tasmania was the most important, followed by the Adelaide Hills. In contrast, the regions of highest relative importance were warmer and drier, such as the Barossa and Hunter Valley. The higher relative importance of slashing and fungicide spraying is the likely due to fungal and weed pressure being greater in cooler wetter regions variables than in drier regions.
\par
The XGBoost ensemble for Region achieved an accuracy of 56.82\% (and 50.58\% validation accuracy). The difference in accuracy compared to the other models is in part due to the large number of classes (58 regions). The ensemble had a great emphasis on area, water, fuel and yield as determining factors (see Figure (\ref{fig:region_sankey}). 
% Although water and diesel were two of the three most frequently occurring variables in predicting region, they were not as connected to the other predictor variables as Yield and area harvested were.
\par
Substantially many of the regions had lower reporting rates, resulting in much poorer classification performance. The regions with the most samples performed the best likely due to the disparity in sample sizes. Bordering regions were routinely grouped together and misclassified as the same region. When scrutinising each class explicitly, the two areas that suffered the most from this were the Limestone Coast (cool coastal areas in South Australia) and the warmer inland regions along the Murray Darling.

@@

This study explored the relationships between vineyard resource use, operations and geographical properties to revenue and operating costs. The analysis was based on a large national study of 6049 samples collected over ten years. Three main findings were identified. First, the most important predictors of revenue and operating costs were fuel, yield and area. Secondly, area and fuel were highly interrelated to other variables (see Figure \ref{fig:operating_costs_sankey} and Figure \ref{fig:revenue_sankey}A). Finally, the relative importance of predictor variables for Region, differed from Revenue and Operating costs, with Water Use being more prominent than Yield. Region was also more prominent than illustrated in the Sankey diagrams due to the relative importance for operating cost and revenue being calculated for individual regions and not all regions together. In its entirety, was the third most important predictor of revenue and the most important predictor for operating costs, relative to the other variables consideration in the analyses.

@@

Warmer regions are known to be beneficial in hastening the ripening process of winegrapes \citep{webbObservedTrendsWinegrape2011}. Warmer regions are also associated with lower quality grapes, caused largely due to this hastened ripening \citep{botting1996canopy}. In general warmer regions are not associated with higher yields, but if a vineyard in a warmer region is sufficiently irrigated much higher yields can be achieved than in cooler regions \citep{campsGrapeHarvestYield2012}. It is likely that the combination of larger vineyards with higher water use is a determining factor in classifying regions which favour larger production of grapes; reflected through region using water use so prominently in the XGBoost ensemble. The link to water resources in defining regions is also an important consideration, as vineyards can leverage higher irrigation rates given more accessible water resources. A further consideration in the link between revenue and region is that grape prices are set at a regional level by buyers \citep{wineaustraliaNationalVintageReport2022}. It is also important to consider that some regions carry particular fame regarding the quality of their produce such as Tasmania, the Hunter Valley and Barossa Valley \citep{hallidayAustralianWineEncyclopedia2009}. This classification can be contrasted with other warmer regions of higher rainfall that use the warmer climate to concentrate their grapes, increasing the flavour profile \citep{goodwinijeriepRegulatedDeficitIrrigation1992,mgmccarthyEffectCropLoad1986}.

@@

In part, some winegrowing strategies are restricted simply through access to water resources. Regions are likely to have varying access to different water sources, such as those along the River Murray being able to utilise river water for crops, unlike most coastal regions which may be drawing from surface or underground water sources. Similarly, the connection between region and fuel use is likely an indicator of the level of infrastructure within the region because vineyards in regions without pressurised water will need to use more fuel to pressurise their irrigation systems.

@@

Separately, revenue and operating cost did have a greater predictability than their counterpart profit (see Appendix). The disparity in accuracy between profit and other economic outcomes is reflective of the complexity in trying to address challenges such as climate change, disease and changing market demands \citep{wineaustraliaNationalVintageReport2020,wineaustraliaNationalVintageReport2021,wineaustraliaNationalVintageReport2022}. The difference between turning a profit or loss is dependent on predictable factors unforecasted factors, farming practice and farmers' decisions. The difference between vineyards that make profit and those that do not could be a multitude of factors including differences in farming practices not captured within this study. Some decisions leading to latent effects such as large scale soil deposition in extreme rain events can be caused by soil compaction due to overworking a vineyard \citep{capelloPermanentCoverSoil2020}.

\iffalse
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  Prior studies have shown that decisions can also have long-lasting positive effects at the cost of short term negatives. In particular the use of cover crops and remedial soil techniques offer such as trade.

@@

This study has provided valuable insights into the multifaceted dynamics governing operational costs and revenue. The impact of different regions highlighted the complex interrelatedness of variables within a vineyard. We relate how factors such as water and fuel intersect to impact operational costs and how different seasonal events affect these operations; as well as the significance of context-specific decision-making. While this investigation utilised a broad regional classification, the potential benefits of adopting a more nuanced approach and incorporating expert knowledge have been highlighted. Further work could pursue causal models and the creation of decision support systems. It is difficult to untangle the predictive and correlative nature of a variable compared to the causal reasons. By delving deeper into the complex interplay of variables, further advancements can be made in optimising vineyard management strategies for lowering operational costs, increasing revenue and enhancing sustainability.

>>>>

 The Australian wine industry is a major contributor to Australia's agricultural sector and economy. As global market demands change and new pressures on the industry present themselves, a more sustainable approach is needed. Through a nationwide data set, collected over ten years, we link key variables in determining vineyard operational costs and revenue through the use of XGBoost. We use a measure of relative importance to show the interrelated nature of these variables and the comparative influence they have on one another. We present these connections through the use of Sankey and Chord diagrams to show the important predictors of revenue and operating costs and their strong interrelatedness. Furthermore, we connect these variables to different wine regions, highlighting the complex influence of location on the use of different resources. The study provides valuable insights into the multifaceted dynamics governing operational costs and revenue, illustrating how factors such as water and fuel use impacts operational costs and how different seasonal events affect these operations.

@@

Historically strong demands for Australian wine have helped to create a thriving industry. However, recent pressures brought on by a loss of tourism and labour due to the COVID-19 pandemic, the global freight crisis, war in Europe, tariffs and rising inflation have negatively affected the industry's outlook \citep{wineaustraliaNationalVintageReport2021,wineaustraliaAustralianWineProduction2021}. The 2021-2022 financial year alone saw a decline of 19\% in exports solely due to tariffs \citep{wineaustraliaNationalVintageReport2022}. A greater understanding of the different underlying conditions leading to improved performance in agricultural productivity and sustainability at scale is key to making data-informed decisions to increase a nation's agricultural sustainability \citep{oecdInnovationProductivitySustainability2019}. Specifically within the Australian wine and vine industry, there is a need to further understand the driving relationships between resource use and economic output, which can help to determine more cost effective and efficient methods and develop benchmarks with local growers \citep{lukemanciniUnderstandingAustralianWine2020}.
\par
An unprecedented amount of data regarding the Australian winegrowing industry has been collected through the Sustainable Winegrowing Australia program, offering the potential for new insights into the driving economic forces of the Australian wine industry. A major part of the potential for insight within this dataset comes from the incorporation of operating costs and grape revenue from grape sales within the data. In this paper, we use data to study economic outcomes and their statistical relationships to vineyards' utilisation of the resources. We further compare the relationships between different resources to address the extensive collinearity found within the data \citep{chenXGBoostScalableTree2016}. We adopt  a popular, relatively new machine learning method, XGBoost, for this analysis because it is able to overcome multicollinearity as well as highlight the level of importance that predictor variables have on response variables.

@@

\subsection{Data}\label{Data}
% 6049 samples - total
% 58 regions
% 10 years
% 
% 853 with reported profits
% 46 regions
% reported since 2018
Data used in this analysis were obtained from Sustainable Winegrowing Australia (SWA), Australia's national wine industry sustainability program. SWA aims to support grape growers and winemakers in demonstrating and improving their sustainability \citep{swaSustainableWingrowingAustralia2022}. Data recorded by SWA are entered manually by winegrowers using a web based interface tool. A total of 6049 observations were collected from 2012/2013 to 2021/2022 financial years, with each observation comprising 23 variables reflecting a vineyard's state for the given year (see Table \ref{tab:vars}). 
\par
\begin{table}[] 
 \label{tab:vars}
 \caption{Summary of variables used in the analysis. The recorded column indicate the number of values that were either greater than zero or that were not missing.}\label{tab:summary}
 \small
 \begin{tabular}{@{}ccccl@{}}
  \toprule
  \textbf{Variable} & \textbf{Units} & \textbf{Recorded} & \textbf{Number of Classes} & \\ \midrule
  Water Used & Mega Litres & 5846 & & \\
  Diesel & Litres & 5585 & & \\
  Biodiesel & Litres & 25 & & \\
  LPG & Litres & 958 & & \\
  Herbicide Spray & Times per year & 2026 & & \\
  Year & Class & 6049 & 10 & \\
  Disease & Class & 6049 & 2 & \\
  Region & Class & 6049 & 58 & \\
  Solar & Kilowatt Hours & 622 & & \\
  Irrigation Type & Class & 6049 & 20 & \\
  Petrol & Litres & 4309 & & \\
  Slashing & Times per year & 2290 & & \\
  Yield & Tonnes & 5935 & & \\
  Irrigation Energy & Class & 6049 & 16 & \\
  Area Harvested & Hectares & 6049 & & \\
  Electricity & Kilowatt Hours & 1014 & & \\
  Insecticide Spray & Times per year & 1092 & & \\
  Fertiliser & KGs of Nitrogen & 795 & & \\
  Fungicide Spray & Times per year & 2260 & & \\
  Cover Crop & Class & 6049 & 32 & \\
  Water Type & Class & 6049 & 39 & \\
  Grape Revenue & AUD & 853 & & \\
  Operating Costs & AUD & 853 & & \\ \bottomrule
  \end{tabular}
\end{table}
\normalsize
The data originally contained only two multiclass variables: year and region. For this case study, related binary variables, such as the use of river water and the use of dam water, were combined to create multiclass variables such as water source. Further details about these variables, their classes and their frequency is available in the Appendix.
\par
The variable Region represented one of the 65 Geographical Indicator Regions (GI Region) used to describe unique localised traits of vineyards across Australia \citep{hallidayAustralianWineEncyclopedia2009,oliverReviewSoilPhysical2013,soarClimateDriversRed2008}. Each region is explicitly defined under the Wine Australia Corporation Act of 1980 \citep{attorney-generalsdepartmentWineAustraliaCorporation2010}.
\par

@@

Region was a highly informative variable based on measures of importance for both operating cost and revenue. As noted above, Region was the third most important variable for determining revenue. The Barossa Valley region and Tasmania were the two most important regions in relation to revenue; these two regions are considered to be some of the highest revenue per hectare regions in Australia \citep{wineaustraliaNationalVintageReport2022}. These two regions are also relative opposites in winegrowing climates with the Barossa having a warm and dry climate focussing on Shiraz grapes and Tasmania having a cool wet climate that favours Pinot/Chardonnay \citep{wineaustraliaNationalVintageReport2022}.
\par
As also noted above, Region was also a key determinant of operating costs. Tasmania had the highest relative importance, followed by the Adelaide Hills. In contrast, the regions of the highest relative importance were warmer and drier, such as the Barossa. The higher relative importance of fungicide spraying is the likely due to fungal pressure being greater in cooler wetter regions variables than in drier regions.
\par
The XGBoost ensemble for Region achieved an accuracy of 56.82\% (and 50.58\% validation accuracy). The difference in accuracy compared to the other models is in part due to the large number of classes (58 regions). The ensemble had an emphasis on area, water, fuel and yield as determining factors (see Figure (\ref{fig:region_sankey}).
% Although water and diesel were two of the three most frequently occurring variables in predicting region, they were not as connected to the other predictor variables as Yield and area harvested were.
\par
A number of regions had lower reporting rates, resulting in much poorer classification performance. The regions with the most samples performed the best likely due to the disparity in sample sizes. Bordering regions were routinely grouped together and misclassified as the same region. When scrutinising each class explicitly, the two areas that effected the most from this were the Limestone Coast (cool coastal areas in South Australia) and the warmer inland regions along the Murray Darling.

@@

This study explored the relationships between vineyard resource use, operations and geographical properties to revenue and operating costs. The analysis was based on a large national study of 6049 samples collected over ten years. Three main findings were identified. First, the most important predictors of revenue and operating costs were fuel, yield and area. Secondly, area and fuel were highly interrelated to other variables (see Figure \ref{fig:operating_costs_sankey} and Figure \ref{fig:revenue_sankey}A). Finally, the relative importance of predictor variables for Region, differed from Revenue and Operating costs, with Water Use being more prominent than Yield. Region was also more prominent than illustrated in the Sankey diagrams due to the relative importance for operating cost and revenue being calculated for individual regions and not all regions together. In its entirety Region was the third most important predictor of revenue and the most important predictor for operating costs, relative to the other variables consideration in the analyses.

@@

Warmer regions are known to be beneficial in hastening the ripening process of winegrapes \citep{webbObservedTrendsWinegrape2011}. Warmer regions are also associated with lower quality grapes, caused largely due to this hastened ripening \citep{botting1996canopy}. It is likely that the combination of larger vineyards with higher water use is a determining factor in classifying regions which favour larger production of grapes; reflected through region using water use so prominently in the XGBoost ensemble. The link to water resources in defining regions is also an important consideration, as vineyards can leverage higher irrigation rates if water resources are available. A further consideration in the link between revenue and region is that grape prices are set at a regional level by buyers \citep{wineaustraliaNationalVintageReport2022}. It is also important to consider that some regions carry particular fame regarding the quality of their produce such as Tasmania, the Hunter Valley and Barossa Valley \citep{hallidayAustralianWineEncyclopedia2009}. This classification can be contrasted with other warmer regions of higher rainfall that use the warmer climate to concentrate their grapes, increasing the flavour profile \citep{goodwinijeriepRegulatedDeficitIrrigation1992,mgmccarthyEffectCropLoad1986}.

@@

In part, yield is sometimes restricted simply through access to water resources. Regions are likely to have varying access to different water sources, such as those along the River Murray being able to utilise river water for crops, unlike most coastal regions which may be drawing from surface or underground water sources. Similarly, the connection between region and fuel use is likely an indicator of the level of infrastructure within the region because vineyards in regions without pressurised water will need to use more fuel or electricity to pressurise their irrigation systems.

@@

Separately, revenue and operating cost did have a greater predictability than their counterpart profit (see Appendix). The disparity in accuracy between profit and other economic outcomes is reflective of the complexity in trying to address challenges such as climate change, disease and changing market demands \citep{wineaustraliaNationalVintageReport2020,wineaustraliaNationalVintageReport2021,wineaustraliaNationalVintageReport2022}. The difference between turning a profit or loss is dependent on predictable factors unforecasted factors, farming practice and farmers' decisions. The difference between vineyards that make profit and those that do not could be a multitude of factors including differences in farming practices not captured within this study.
\iffalse
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  Prior studies have shown that decisions can also have long-lasting positive effects at the cost of short term negatives. In particular the use of cover crops and remedial soil techniques offer such as trade.

@@

This study has provided valuable insights into the multifaceted dynamics governing operational costs and revenue in vineyards. The impact of different regions highlighted the complex interrelatedness of variables within a vineyard. We relate how factors such as water and fuel intersect to impact operational costs and how different seasonal events affect these operations; as well as the significance of context-specific decision-making. While this investigation utilised a broad regional classification, the potential benefits of adopting a more nuanced approach and incorporating expert knowledge have been highlighted. Further work could pursue causal models and the creation of decision support systems. It is difficult to untangle the predictive and correlative nature of a variable compared to the causal reasons. By delving deeper into the complex interplay of variables, further advancements can be made in optimising vineyard management strategies for lowering operational costs, increasing revenue and enhancing sustainability.
